\textbf{Influence of galaxy rotation and outflows \\ in the Lyman Alpha spectral line}

### 2016-02-04 abstract/abstract.tex
spanish abstract updated

\author{Maria Camila Remolina-Gutierrez$^1$, Jaime E. Forero-Romero$^1$\\
	    mc.remolina197@uniandes.edu.co, \hspace{0.8mm} je.forero@uniandes.edu.co\\ 
		$^1$ Departamento de F\'{i}sica, Universidad de los Andes \\
		Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\date{} % <--- leave date empty
\maketitle\thispagestyle{empty} %% <-- you need this for the first page
\textit{\textbf{Keywords - Galaxies: high-redshift, Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows, Radiative Transfer.}}\\

@@

\bibliographystyle{latex/apj}
\bibliography{references}

>>>>

\author{Maria Camila Remolina-Gutierrez$^1$, Jaime E. Forero-Romero$^1$\\ \vspace{3mm}
	    mc.remolina197@uniandes.edu.co, \hspace{0.8mm} je.forero@uniandes.edu.co\\ 
		$^1$ Departamento de F\'{i}sica, Universidad de los Andes \\
		Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\date{} % <--- leave date empty
\maketitle\thispagestyle{empty} %% <-- you need this for the first page
\textit{Keywords - Galaxies: high-redshift, Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows, Radiative Transfer.}\\

@@

\bibliographystyle{apj}
\bibliography{references}
